The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-15 methods/ms.tex
some more paper modifications plus.... crap, forgot to add plot_crs

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution.]
{\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping1}
      \caption{An example of the change in the time series as
      iterative mapping proceeds.}
    \end{center}
    \label{fig:IterativeMapping}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping2}
      \caption{}
    \end{center}
    \label{fig:IterativeMapping-b}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping3}
      \caption{}
    \end{center}
    \label{fig:IterativeMapping-c}
  \end{minipage}
\end{figure}

% -----------------------------------------------------------------------------
\setcounter{subfig}{1}
\begin{figure}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_withglitch}
    \end{center}
  \end{minipage}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_glitchgone}
    \end{center}
  \end{minipage}
  \caption{An illustration of the flagging process using the waterfall
plot. Left: The glitch apparent at middle right is the same one whose
time series is shown in Figure \ref{fig:CosmicRayGlitch}.  Because of
the PCA subtraction, the effect of the glitch also propagates over the
other bolometers, appearing as a horizontal stripe. Right: The same
data displayed with the time point including the glitch flagged out
and rescaled}

@@

  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_plots}
      \caption{An illustration of a ``glitch'' in a single bolometer
timestream (red) due to a cosmic ray strike.  Note the acausal ringing
due to the application of the downsampling filter.  The time series
for a physically adjacent bolometer is shown in blue, and a bolometer
which does not pass over a source in green.  The PCA model has already
been subtracted from the data.}
    \end{center}
  \end{minipage}

>>>>

  \subfigure[The residuals of the pointing model.  Note the Gaussian
distribution. ($\sigma = 5.94,2.92$)]
{\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping1}
      \caption{An example of the change in the time series as
      iterative mapping proceeds.  1. Raw time series 2. After removal
      of residual 60Hz signal 3. Exponential decay function at scan
      turnarounds subtracted 4. A polynomial (with astrophysical source
      rejection) is fit to remove large-scale variations across the scan. }
    \end{center}
    \label{fig:IterativeMapping}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping2}
      \caption{Panel 1 is the same as panel 4 in the previous figure.
      Before the first cleaning, the raw data (black) and remainder data (green)
      are equal because there is no model.  
      Panel 2 shows the median-atmosphere subtraction, which is the first-
      order correction.
      Panel 3 shows the astrophysical signal left over from the PCA selection.
      Panel 4 shows the total atmosphere model from PCA and median estimation}
    \end{center}
    \label{fig:IterativeMapping-b}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.9]{iterative_mapping3}
      \caption{Same as previous figure, except after 20 iterations.
      Panel 1 - The deconvolved astrophysical map is returned to a timestream (red)
      and subtracted from the 'raw' data (black). 
      Panel 2 - The median of the remainder (green) is subtracted as the first
      atmosphere estimation
      Panel 3 - The cumulative astrophysical model (red) and the additional astrophysical
      signal from iteration 20 (black)
      Panel 4 - The atmosphere signal after 20 iterations}
    \end{center}
    \label{fig:IterativeMapping-c}
  \end{minipage}
\end{figure}

% -----------------------------------------------------------------------------
\setcounter{subfig}{1}
\begin{figure}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_withglitch}
    \end{center}
  \end{minipage}
  \begin{minipage}{3.25in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_glitchgone}
    \end{center}
  \end{minipage}
  \caption{An illustration of the flagging process using the waterfall plot.
  Left: The glitch apparent at middle right (bolometer 98, around 6.2s) is the
  same one whose time series is shown in Figure \ref{fig:Flagger}b.  Because of
  the PCA subtraction, the effect of the glitch also propagates over the other
  bolometers, appearing as a horizontal stripe. Right: The same data displayed
  with the time point including the glitch flagged out and rescaled}

@@

  \begin{minipage}{6.5in}
    \begin{center}
      \includegraphics[scale=0.5]{flagger_plots}
      \caption{An illustration of a ``glitch'' in a single bolometer timestream
      (red) due to a cosmic ray strike.  Note the acausal ringing due to the
      application of the downsampling filter.  The time series for a physically
      adjacent bolometer is shown in blue, and a bolometer which does not pass
      over the source in green.  The PCA atmosphere estimation has already been
      subtracted from the data.}
    \end{center}
  \end{minipage}
